% This is a test document for reLyX.pl
\documentclass[11pt]{article} %some comments

%comments
\def\blah{\blahblah}
% And more comments

%more comments
\begin{document}

\title{Test Document}
\maketitle
\tableofcontents

\section{First Section}
This {\large a {\small b \tiny c} \huge d} is some text. %Midline comment
\framebox[3in][s]{What are you doing \ldots Dave}. This is more text.

\section*{MySection}
\label{sec:mysection}This is some ``quoted'' text in a new section.
I {\em am\footnote{This is a great footnote because:
\begin{itemize}
\item The footnote is not \emph{emphasized}.
\item The text is
\end{itemize}

How cool is that!?} emphasizing ``text.

I keep'' emphasizing}. This ~ is text in a new par\-agraph.\\ It has \ldots
an $ \alpha $ in it, which is OK\@. I can type special
characters\footnote{i.e., characters which must be escaped}
like \& and \#.

\_ is a neat token.
% This line won't print!

Now I \textsf{want \texttt{to} write} some math in a displayed equation.
\begin{eqnarray*}
q^{(i)}_O & = & q^{water}_{O}+dq_{O}\times (P_{deg}^{(i-1)}-P_{deg}^{(i)})\\
q_{H}^{(i)} & = & q^{water}_{H}+dq_{H}\times (P_{deg}^{(i-1)}-P_{deg}^{(i)})\\
q_{p}^{(i)} & = & q^{water}_{H}+dq_{H}\times (P_{deg}^{(i-1)}-P^{(i+1)}_{deg})
\end{eqnarray*}

Here's an itemized list
\begin{itemize}
\item this is an item
\begin{enumerate}
\item this is a numbered item

But now I want to write some text.
\item this is another numbered item

More text
\end{enumerate}
Yet more text

\item this is another unnumbered item

Final text
\end{itemize}

\section[hi]{New Section}
Here's a {\em quotation:
\begin{quotation}
Hello there how are you?

I am fine. Thanks
\end{quotation}

This} is a reference to section \ref{sec:mysection} on page
\pageref{sec:mysection}.

\begin{tabular}{ll}
foo & bar \\
bar & foo
\end{tabular}

Final Text.
\end{document}



